A Lattice Boltzmann Method for immiscible multiphase flow simulations using the Level Set Method

### 2015-08-19 Vortrag/folien.tex
Folien

\begin{itemize}
\item<1-> $N$ immiscible fluids.
\item<2-> Each has own $\rho_i, \nu_i$
\item<3-> Hydrodynamics described by (incompressible) NSE
\end{itemize}
\visible<3->{
$$
\nabla \cdot  \vec v = 0
$$
$$
\frac{\partial \vec v}{\partial t} + \left(\vec  v \cdot \nabla \right) \vec v
=
-\frac{1}{\varrho_i}\nabla p + \nu_i \nabla^2 \vec v $$
}
\end{frame}

@@

\begin{frame}
\visible<1->{
$\tilde{v}$ is calculated by linear interpolation:
$$\tilde{v} = q v (x_2,t) + (1-q) v(x_1,t)$$
}
\visible<2->{
$R_i$ consists of several parts:
$$R_i = 6 \Delta x^2 f_{i}^{*} {\Lambda}_i : A$$
}
\visible<3->{
\begin{itemize}
\item<3-> with:
$$ {\Lambda}_i = c_i \otimes c_i - \frac13 {|c_i|}^2 \mathbb{I}$$
$$ A = -q(1-q)[S] - (q - 1/2) S^{2} + O(\Delta x)$$
\item<4-> $S^{(k)}$ velocity gradient at $x_k$
\item<5-> $[S] = \lim_{\epsilon \to 0}(S(x+\epsilon \vec n) -S(x-\epsilon \vec n))$ jump of velocity gradient at the interface. Depends on normal, tangent and curvature.
\end{itemize}
}
\end{frame}

@@

\vspace{.8cm} 
Outlook:
\begin{itemize}
\item<1-> Add correction term to prevent mass loss
\item<2-> Reduce computational effort: Store Level-Set function only in narrow band around interface, Adalsteinsson and Sethian
\item<3-> $\rightarrow$ \dots ?
%TODO: Quellen als Footnotes + Uebersichtsfolie
%\item<3-> Include thermal flow (simulate e.g. lava lamp) / Include gravity
\end{itemize}

>>>>

\begin{itemize}
\item<1-> $N$ immiscible fluids.
\item<2-> Each has own $\rho_i, \nu_i$
\item<3-> Hydrodynamics described by (incompressible) NSE
\end{itemize}
\visible<3->{
$$
\nabla \cdot  \vec v_i = 0 \text{  in } \Omega_i
$$
$$
\frac{\partial \vec v_i}{\partial t} + \left(\vec  v _i\cdot \nabla \right) \vec v_i
=
-\frac{1}{\varrho_i}\nabla p_i + \nu_i \nabla^2 \vec v_i \text{  in } \Omega_i
$$
}
\end{frame}

@@

\begin{frame}
\visible<1->{
$\tilde{v}$ is calculated by linear interpolation:
$$\tilde{v} = q v (x_2,t) + (1-q) v(x_1,t)$$
}
\visible<2->{
$R_i$ consists of several parts:
$$R_i = 6 \Delta x^2 f_{i}^{*} {\Lambda}_i : A$$
}
\visible<3->{
\begin{itemize}
\item<3-> with:
$$ {\Lambda}_i = c_i \otimes c_i - \frac13 {|c_i|}^2 \mathbb{I}$$
$$ A = -q(1-q)[S] - (q - 1/2) S^{2}$$
\item<4-> $S^{(k)}$ velocity gradient at $x_k$
\item<5-> $[S] = \lim_{\epsilon \to 0}(S(x+\epsilon \vec n) -S(x-\epsilon \vec n))$ jump of velocity gradient at the interface. Depends on normal, tangent and curvature.
\end{itemize}
}
\end{frame}

@@

\vspace{.8cm} 
Outlook:
\begin{itemize}
\item<1-> Create more examples
\item<2-> Add correction term to prevent mass loss
\item<3-> Reduce computational effort: Store Level-Set function only in narrow band around interface, Adalsteinsson and Sethian
%TODO: Quellen als Footnotes + Uebersichtsfolie
%\item<3-> Include thermal flow (simulate e.g. lava lamp) / Include gravity
\end{itemize}
